Appendix to ``Understanding both enhanced and impaired learning with enhanced plasticity: a saturation hypothesis''

### 2016-12-03 MHCpaper/MHCsupp.tex
surya's edits

For the non-uniform multistate model, we see that the \KO\ models are slower than wild-type without pre-training, as seen experimentally.
This seems to be because the enhanced depression results in a greater fraction of synapses begin in states of weaker synaptic weight %(see \autoref{fig:nonuni}\ref{fig:nonuni_eq}\ref{fig:nonuni_eq_KO})
where the depressing transitions have lower probability (see \autoref{fig:models}\ref{fig:nonuni_model}).

>>>>

For the non-uniform multistate model, we see that the \KO\ models are slower than wild-type without pre-training, as seen experimentally.
This seems to be because the enhanced depression results in a greater fraction of synapses starting in states of weaker synaptic weight %(see \autoref{fig:nonuni}\ref{fig:nonuni_eq}\ref{fig:nonuni_eq_KO})
where the depressing transitions have lower probability (see \autoref{fig:models}\ref{fig:nonuni_model}).
